Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-09-25 methodology.tex
2016-08-24
todo

The meteorological stations of Corbana acquire data every five
minutes.
%
\todofn{However, for the current study weekly averages were used,}
{Hay que explicar por qué? $\rightarrow$ reducción de ruido, etc.}
%
computed on the data collected by nearby stations in each farm.

@@

  Dijiste que las variables se promedian para una semana.  ¿Qué
  significan entonces las variables que dicen ``mean''?
}

>>>>

The meteorological stations of Corbana acquire data every five
minutes.
%
\todofn{However, for the current study weekly data were used.}
{Hay que explicar por qué? $\rightarrow$ reducción de ruido, etc.}
%
computed on the data collected by nearby stations in each farm. Experiments were carry out with daily periodicity in meteorological variables and the results proved do not improve the prediction. Besides, weekly data pretend to diminish noise due sensor accuracy, missing values and outliers no detected.

@@

  Dijiste que las variables se promedian para una semana.  ¿Qué
  significan entonces las variables que dicen ``mean''?

  COMENTARIO: Modifiqué estas explicaciones para que quedara más claro el detalle de las variables.  Me dirás qué te parece, si las dejamos así o amplío.
}
